---
title: "Weight of Fish"
author: "Daniel Purri"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch


```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~ . ,
                          data = Perch,
                          nbest = 1, 
                          nvmax = NULL, 
                          force.in = NULL, force.out = NULL, 
                          method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```


```{r}
library(car)
subsets(regsubsets.out, statistic="adjr2", legend="bottom", main="adjr2")
```


### Best Models

The best model is two element model. H and W model

### Best Two regressor model

For this one is also H and W model.

## Pike

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~ . ,
                          data = Pike,
                          nbest = 1, 
                          nvmax = NULL, 
                          force.in = NULL, force.out = NULL, 
                          method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

```{r}
library(car)
subsets(regsubsets.out, statistic="adjr2", legend="bottom", main="adjr2")
```



### Best Models

Best model is model5

### Best Two regressor model

Best model is model3

The best model is different to the best two regressor model so we will run ANOVA.

```{r}
model5 = lm(Weight ~ ., data = Pike)
summary.lm(model5)

model2 = lm(Weight ~ Length2 + Height + Width, data = Pike)
model3 = lm(Weight ~ Length2 + Height, data = Pike)

anova(model5, model2)
```


```{r}
library(car)
subsets(regsubsets.out, statistic="adjr2", legend="bottom", main="adjr2")
```


## Roach

### Best Models

Seems like the best model is model 2, where we can find L3 and W.

### Best Two regressor model

The best model and the best regressor model are both the same, being model 2= L3-W.

## Final Summary Statements

For Perch and Roach the best models and the best two regressor models are the same; the model 2 for
both of them so we didn't have to compare or use ANOVA to find the p-value.